---
title: "Untitled"
author: "Irina Klein"
date: "11/26/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(caret)
library(tree)
```

## Category

Perhaps we should remove the observations for which the category of the issue is not one of the frequent ones.

```{r}
setwd("~/CSP571ProjectGroup")
df <- read_csv("df.csv")
## category
#df  %>% group_by(category) %>% summarise(n = n(), share = round(n()/114660,3)) %>% arrange(n) 

## subcategory
#n <- df  %>% group_by(subcategory) %>% summarise(n = n(), share = round(n()/114660,3)) %>% arrange(n) 

## both
(keepnum <- df  %>% group_by(category, subcategory) %>% summarise(n = n(), share = round(n()/114660,3)) %>% arrange(n) %>% filter(share > 0.005) %>% summarise(n = sum(n)) %>% summarise(n = sum(n)) )

 keepnum/nrow(df)
 
df_75 <- df %>%
group_by(category, subcategory) %>%
mutate(m = n()/114660) %>%
ungroup() %>%
filter(m > 0.005)
```

If we remove all the observations for which category&subcategory combinations appear in less than in 0.5% observations, we end up with 76% of observations.


# Tree methods 

```{r}
# test run on the first 1000 rows
df_1000 <- df_75[1:1000,]

#as.factor
cols <- c("made_sla", "category", "incident_state", "contact_type", "subcategory", "urgency", "impact","priority", "problem_id")
df_1000[cols] <- lapply(df_1000[cols], factor)

#tree
tree.incs <- tree(resolved_updated_diff ~ . -number-m-sys_updated_by, df_1000)
summary(tree.incs)
tree.incs
```

The deviance is very large, meaning that the predictions would not be accurate.
We will classify all the resolutions time to a specified set of buckets (<2h, <1day, ect.) and build a classification tree. 

