---
title: "dataframe for analysis"
author: "Irina Klein"
date: "10/31/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Data uploading and cleaning

```{r}
setwd("~/CSP571ProjectGroup")
incident_event_log <- read_csv("incident_event_log_difftime.csv", na = c("?", "NA"))
print(incident_event_log,width = 1000,n = 5)
```

We will only consider observations that have incident_state != 'Closed', since we want to predict the resolution time while incident is still not closed. To check whether all the incidents in the dataset are closed:

```{r}
#group rows by status
incident_event_log %>% group_by(incident_state) %>% summarise(n = n())

# number of unique incs where state != 'closed'
incident_event_log %>%  filter(incident_state != 'Closed') %>% group_by(number) %>% summarise(n = n()) %>% summarise(n = n()) 

# number of unique incs where state == 'closed'
incident_event_log %>%  filter(incident_state == 'Closed') %>% group_by(number) %>% summarise(n = n()) %>% summarise(n = n())

#note that incident can be closed more than once 
incident_event_log %>%  filter(incident_state == 'Closed')  %>% summarise(n = n()) 

closed_more_than_once <- incident_event_log %>%  filter(incident_state == 'Closed') %>% group_by(number) %>% summarise(n = n()) %>% filter(n > 1) %>% select(number)
closed_more_than_once_v <- as.vector(t(closed_more_than_once))
```

According to [ITIL Incident Management standards](https://en.wikipedia.org/wiki/Incident_management_(ITSM)), incidents should not be closed more than once. We will consider the cases when incident is in status 'closed' more than once as exceptions and will exclude them from the analysis. 

Incidents with status logs = '-100' we will replace with 'Active' status, since they are not closed and -100 does not seem to have a special meaning. 
```{r}
# number of unique incs where state == '-100'
incident_event_log %>%  filter(incident_state == '-100') %>% group_by(number) %>% summarise(n = n()) 
incident_event_log %>% filter(number == 'INC0028089')
incident_event_log %>% filter(number == 'INC0030413')
```


The final data set in terms of the observations: 
```{r}
incident_event_log <- incident_event_log %>%
     mutate(incident_state = replace(incident_state, incident_state == '-100', 'Active'))  %>% 
     filter(!number %in% closed_more_than_once_v) %>% 
    filter(!incident_state == 'Closed')

#group rows by status
incident_event_log %>% group_by(incident_state) %>% summarise(n = n())
```


We will remove the columns: active,caller_id, opened_by, opened_at, sys_created_at, sys_created_by, sys_updated_at, cmdb_ci, notify, u_priority_confirmation, rfc, caused_by, vendor, resolved_by, resolved_at, closed_at
```{r}
## active columns
incident_event_log %>% group_by(active) %>% summarise(n = n())
incident_event_log %>% filter(active == FALSE) # error
incident_event_log %>% filter(incident_state == 'Resolved')

## caller_id - can differ
incident_event_log %>% group_by(caller_id) %>% summarise(n = n())

## opened_by - does not matter in our analysis
incident_event_log %>% group_by(opened_by) %>% summarise(n = n())

## sys_created_by - as factor. Support engineer who submitted the **first** log.
incident_event_log %>% group_by(sys_created_by) %>% summarise(n = n())

## sys_created_by - as factor. Support engineer who submitted the **first** log.
incident_event_log %>% group_by(sys_created_by) %>% summarise(n = n())

## cmdb_ci - unknown attribute
incident_event_log %>% group_by(cmdb_ci) %>% summarise(n = n())

## u_priority_confirmation - unknown attribute
incident_event_log %>% group_by(u_priority_confirmation) %>% summarise(n = n())

## notify
incident_event_log %>% group_by(notify) %>% summarise(n = n())

## rfc - unknown attribute
incident_event_log %>% group_by(rfc) %>% summarise(n = n())

## vendor - does not seem relevant in the analysis.
incident_event_log %>% group_by(vendor) %>% summarise(n = n())

## caused_by - all NAs
incident_event_log %>% group_by(caused_by) %>% summarise(n = n())


```

We will exclude for now (might consider later): location, u_symptom, knowledge

```{r}
## location - does not seem relevant in this analysis. There are NAs.
incident_event_log %>% group_by(location) %>% summarise(n = n())

## u_symptom - seems to an additional note that may or may not be included in an incident. There are 26K NAs.
incident_event_log %>% group_by(u_symptom) %>% summarise(n = n())
incident_event_log %>% group_by(category, subcategory,u_symptom ) %>% summarise(n = n())

## knowledge - unknown attribute
incident_event_log %>% group_by(knowledge) %>% summarise(n = n())

```


Keep for analysis: number, incident_state, reassignment_count, reopen_count, sys_mod_count, made_sla, sys_updated_by, contact_type, category, subcategory.

```{r}
## reassignment_count - change of group
incident_event_log %>% filter(number == 'INC0000065') %>% select(number, incident_state, reassignment_count, assignment_group)

## reopen_count - after status 'resolved'
incident_event_log %>% filter(reopen_count != 0)
incident_event_log %>% filter(number == 'INC0000294') %>% select(number, incident_state, reopen_count)

## sys_mod_count - each new log 
incident_event_log %>% filter(sys_mod_count != 0)
incident_event_log %>% filter(number == 'INC0000047') %>% select(number, incident_state, sys_mod_count)

    # note: sys_mod_count is not always +1. Will leave as is.
    incident_event_log %>% filter(number == 'INC0000045') %>% select(number, incident_state, sys_mod_count)

## made_sla - not that many observations
incident_event_log %>% group_by(made_sla) %>% summarise(n = n())
incident_event_log %>% filter(made_sla == FALSE)

## sys_updated_by - as factor. Support engineer who submitted the log. Will assume that the engineers will stay the same.
incident_event_log %>% group_by(sys_updated_by) %>% summarise(n = n())

## contact_type - factor
incident_event_log %>% group_by(contact_type) %>% summarise(n = n())

## category - factor. There are NAs.
incident_event_log %>% group_by(category) %>% summarise(n = n())

## subcategory - factor. One subcategory can appear on more than one category. Should be analysed separately from category.
#There are NAs.
incident_event_log %>% group_by(category, subcategory) %>% summarise(n = n()) %>% group_by(subcategory) %>% summarise(n = n()) %>% filter(n >1)

incident_event_log %>% group_by(category, subcategory) %>% summarise(n = n()) %>% filter(subcategory == 'Subcategory 102')
incident_event_log %>% group_by(category, subcategory) %>% summarise(n = n()) %>% filter(subcategory == 'Subcategory 177')

## urgency
incident_event_log %>% group_by(urgency) %>% summarise(n = n())

## priority
incident_event_log %>% group_by(priority) %>% summarise(n = n())

## impact
incident_event_log %>% group_by(impact) %>% summarise(n = n())
```

Transform for analysis: problem_id,
```{r}
## problem_id - turn to Boolean: problems exists or not
incident_event_log %>% group_by(problem_id) %>% summarise(n = n())
```

Final data set in terms of the predictor variables: 
```{r}
incident_event_log <- incident_event_log %>%
    select(number, incident_state,reassignment_count, reopen_count, sys_mod_count, made_sla, sys_updated_by, contact_type, category, subcategory, problem_id,resolved_updated_diff ) %>%
     mutate(problem_id = if_else(is.na(problem_id),0,1))
head(incident_event_log)
```

## NAs

In the resulting dataframe the only variables with missing values are the category and subcategory columns. Even though for some of the observations we could assume the category is the same as in later observations for the same incident, we will not do that. Since it is possible for an incident to be created without a category/subcategory we will treat NA as a separate factor (base factor).
```{r}
colSums(is.na(incident_event_log))
incident_event_log %>% filter(is.na(category))
incident_event_log %>% filter(number == 'INC0108121')

incident_event_log  <- incident_event_log %>%
    mutate(category = replace(category, is.na(category), "None"), subcategory = replace(subcategory, is.na(subcategory), "None")) 

```


## Save dataframe


```{r}
#setwd("~/CSP571ProjectGroup")
#write_csv(incident_event_log, "df.csv")

```

